An Efficient Minibatch Acceptance Test for Metropolis-Hastings

### 2016-09-30 nips_2016.tex
Revised Figure 5, updated captions. Also gitignore to make our lives easier

\begin{figure}[t]
    \centering
    \includegraphics[width=1\linewidth]{minibatch_size_gaussian.png}
    \caption{
    Histograms of minibatch sizes for the three methods used in
    Section~\ref{ssec:gaussians}. Note the log-log scale, to facilitate
    comparisons across methods; in particular, the axes have the same
    range.
    }
    \label{fig:gauss_mix_2}
\end{figure}

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=1\linewidth]{LogisticRegressionResult/minibatch_size_logistic.png}
	\caption{
    Counts of minibatch sizes needed for the three methods in the MNIST
    classification task.
    }
	\label{fig:logistic_minibatch}
\end{figure}

>>>>

\begin{figure}[t]
    \centering
    \includegraphics[width=1\linewidth]{minibatch_size_gaussian.png}
    \caption{
    Counts of minibatch sizes that the three methods used in the experiment of
    Section~\ref{ssec:gaussians}. To make comparisons easier, the axes have the
    same range (using a log-log scale).
    }
    \label{fig:gauss_mix_2}
\end{figure}

@@

\begin{figure}[t]
	\centering
	\includegraphics[width=1\linewidth]{minibatch_size_logistic.png}
	\caption{
    Counts of minibatch sizes that the three methods used in the logistic
    regression experiment from Section~\ref{ssec:logistic}. It is analogous to
    Figure~\ref{fig:gauss_mix_2}.
    }
	\label{fig:logistic_minibatch}
\end{figure}
